An Overview on Temporal Databases.\\ New Approaches and Proposals.

### 2012-02-17 trunk/book/sources/fuzzyTemporalDatabases.tex
fix: all the definitions are in a svgraybox and start with a capital letter.

\begin{definition}
\textbf{(query specification)}
A query $\tilde{Q}$ is given by:
\begin{equation}
\label{eq:query-specification}
\tilde{Q} = \left( Q^{time}, Q \right)
\end{equation}
Here $Q = \left \lbrace q_1, \cdots, q_n \right \rbrace$ are the possibly fuzzy non-temporal constraints and $Q^{time}$ are the temporal constraints specified in the query:
\end{definition}

%%specify better this:
%\begin{svgraybox}
%\begin{definition}
%\label{def:query-constraint}
%\textbf{(query constraint)}
%$Q$ is the 
%A query constraint $q_a$ for an attribute $a$ with attribute domain $\mathcal{D}$, is a restriction in the subset of the values in the attribute domain:
%\begin{equation}
%\label{eq:query-constraint}
%q_a = \left \lbrace d \mid d \subseteq \mathcal{D} \right \rbrace
%\end{equation}
%\end{definition}

\begin{definition}
\textbf{(temporal query specification)}
$Q^{time}$ is defined by:
\begin{equation}
Q^{time} = \left( I,AR \right)
\end{equation}
Where $I$ is a crisp time interval and $AR$ is one of the Allen's relations, see table \ref{tab:fuzzy-allen-relations}. The interpretation is that given an ill-known time interval $J$, the user request the set of records in which $I$ AR $J$ hold.
\end{definition}

@@

\begin{definition}
\label{def:evaluation-function}
\textbf{(evaluation function)}
An evaluation function $e_{Q} \left( r \right)$ is a mapping from the attribute value from the row $r$ in the database with respect to the constraints $Q = \left \lbrace q_1, \cdots, q_n \right \rbrace$ to the unit interval $\left[ 0,1 \right]$. 
\begin{equation}
\label{eq:evaluation-function} 
e_{Q} = t \mid t \in \left[ 0,1 \right]
\end{equation}
\end{definition}

>>>>

\begin{svgraybox}
\begin{definition}
\textbf{Query specification}
A query $\tilde{Q}$ is given by:
\begin{equation}
\label{eq:query-specification}
\tilde{Q} = \left( Q^{time}, Q \right)
\end{equation}
Here $Q = \left \lbrace q_1, \cdots, q_n \right \rbrace$ are the possibly fuzzy non-temporal constraints and $Q^{time}$ are the temporal constraints specified in the query:
\end{definition}
\end{svgraybox}
%%specify better this:
%\begin{svgraybox}
%\begin{definition}
%\label{def:query-constraint}
%\textbf{(query constraint)}
%$Q$ is the 
%A query constraint $q_a$ for an attribute $a$ with attribute domain $\mathcal{D}$, is a restriction in the subset of the values in the attribute domain:
%\begin{equation}
%\label{eq:query-constraint}
%q_a = \left \lbrace d \mid d \subseteq \mathcal{D} \right \rbrace
%\end{equation}
%\end{definition}

\begin{svgraybox}
\begin{definition}
\textbf{Temporal query specification}
$Q^{time}$ is defined by:
\begin{equation}
Q^{time} = \left( I,AR \right)
\end{equation}
Where $I$ is a crisp time interval and $AR$ is one of the Allen's relations, see table \ref{tab:fuzzy-allen-relations}. The interpretation is that given an ill-known time interval $J$, the user request the set of records in which $I$ AR $J$ hold.
\end{definition}
\end{svgraybox}

@@

\begin{svgraybox}
\begin{definition}
\label{def:evaluation-function}
\textbf{Evaluation function}
An evaluation function $e_{Q} \left( r \right)$ is a mapping from the attribute value from the row $r$ in the database with respect to the constraints $Q = \left \lbrace q_1, \cdots, q_n \right \rbrace$ to the unit interval $\left[ 0,1 \right]$. 
\begin{equation}
\label{eq:evaluation-function} 
e_{Q} = t \mid t \in \left[ 0,1 \right]
\end{equation}
\end{definition}
\end{svgraybox}

### 2012-02-17 trunk/book/sources/timeDomain.tex
fix: all the definitions are in a svgraybox and start with a capital letter.

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{(Instant)}\\
An \emph{\textbf{instant}} is a time point on an underlying time axis.
\end{definition}
\vspace{-10pt}
\end{svgraybox}

@@

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{(Granularity)}\\
A \emph{\textbf{granularity}} is an ordered set of non-overlapping and continuous temporal elements called \emph{granules}.
\end{definition}

\begin{definition}\textbf{(Granule)}\\
A \textbf{\emph{granule}} is the basic time unit in a granularity.
\end{definition}
\vspace{-10pt}
\end{svgraybox}

@@

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{(Finner Than)}\\
Consider a mapping function $f$ and let $i_G$ and $j_H$ be elements of granularities $G$ and $H$ respectively. Granularity $G$ is now said to be \emph{\textbf{finner than}} granularity $H$ if:
\begin{equation}
\label{eq:finner-than}
| f \left( i_G \right) |\ <\ |  f \left( j_H \right)| \nonumber
\end{equation} 
\end{definition}

\begin{definition}
\label{def:coarser-than}\textbf{(coarser than)}
Consider a mapping function $f$ and let $i_G$ and $j_H$ be elements of granularities $G$ and $H$ repectively. Granularity $G$ is now said to be \emph{\textbf{coarser than}} granularity $H$ if:
\begin{equation}
\label{eq:coarser-than}
| f \left( i_G \right)|\ >\ |  f \left( j_H \right)| \nonumber
\end{equation} 
\end{definition}
\vspace{-10pt}
\end{svgraybox}

@@

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{(Linear Hierarchy of Granularities)}\\
A \emph{\textbf{linear hierarchy of granularities}} is a finite set of granularities with a linear order (denoted $\sqsubset$). The most coarse granularity is called \emph{the top of the hierarchy} and must be an infinite set while all other granularities must be finite sets.
\end{definition}
\vspace{-10pt}
\end{svgraybox}

@@

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{(Linear Calendar)}\\
A \emph{\textbf{linear calendar}} consist of a linear hierarchy of granularities and a validity predicate which specifies if a granule is valid in the calendar.
\end{definition}
\vspace{-10pt}
\end{svgraybox}

>>>>

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{Instant}\\
An \emph{\textbf{instant}} is a time point on an underlying time axis.
\end{definition}
\vspace{-10pt}
\end{svgraybox}

@@

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{Granularity}\\
A \emph{\textbf{granularity}} is an ordered set of non-overlapping and continuous temporal elements called \emph{granules}.
\end{definition}

\begin{definition}\textbf{Granule}\\
A \textbf{\emph{granule}} is the basic time unit in a granularity.
\end{definition}
\vspace{-10pt}
\end{svgraybox}

@@

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{Finner Than}\\
Consider a mapping function $f$ and let $i_G$ and $j_H$ be elements of granularities $G$ and $H$ respectively. Granularity $G$ is now said to be \emph{\textbf{finner than}} granularity $H$ if:
\begin{equation}
\label{eq:finner-than}
| f \left( i_G \right) |\ <\ |  f \left( j_H \right)| \nonumber
\end{equation} 
\end{definition}

\begin{definition}
\label{def:coarser-than}\textbf{Coarser Than}
Consider a mapping function $f$ and let $i_G$ and $j_H$ be elements of granularities $G$ and $H$ repectively. Granularity $G$ is now said to be \emph{\textbf{coarser than}} granularity $H$ if:
\begin{equation}
\label{eq:coarser-than}
| f \left( i_G \right)|\ >\ |  f \left( j_H \right)| \nonumber
\end{equation} 
\end{definition}
\vspace{-10pt}
\end{svgraybox}

@@

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{Linear Hierarchy of Granularities}\\
A \emph{\textbf{linear hierarchy of granularities}} is a finite set of granularities with a linear order (denoted $\sqsubset$). The most coarse granularity is called \emph{the top of the hierarchy} and must be an infinite set while all other granularities must be finite sets.
\end{definition}
\vspace{-10pt}
\end{svgraybox}

@@

\begin{svgraybox}
\vspace{-10pt}
\begin{definition}\textbf{Linear Calendar}\\
A \emph{\textbf{linear calendar}} consist of a linear hierarchy of granularities and a validity predicate which specifies if a granule is valid in the calendar.
\end{definition}
\vspace{-10pt}
\end{svgraybox}
